---
title: "Movie_Data"
author: "Michael Candella"
date: "March 27, 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Movie Analysis
  Here is a Sample of Movie Analysis, for my data I decided to take all oscar nominated films from rotten tomatoes and painstakingly sort them by genre, rotten tomatoes score, year, decade, and title. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(readr)
Movie <- read_csv("Movie.csv")
library(ggplot2)
library(plotly)
library(dplyr)

Decade<-Movie$Decade
Name<-Movie$Name
Critic<-Movie$RT_Score
Audience<-Movie$A_Score
Genre<-Movie$Genre


Movie %>%
plot_ly(x= ~Critic,y=~Audience, color = ~Genre,hoverinfo="text",
        text=~paste("Movie Title:",Name,"<br>","RT Score:",Critic,"<br>","Audience Score:",Audience,"<br>","Genre:",Genre))%>%
  add_markers()%>%
  layout(title="Audience Scores and RT Scores for Oscar Nominated Films (1980-2018)")

Drama<-Movie%>%
  filter(Movie$Genre=="Drama")

Action<-Movie%>%
  filter(Movie$Genre=="Action")

```
```{r echo=FALSE, message=FALSE, warning=FALSE}
P1<-Drama%>%
plot_ly(x=~Drama$RT_Score,y=~Drama$A_Score,color = ~Drama$Decade,hoverinfo="text",
        text=~paste("Movie Title:",Drama$Name,"<br>","RT Score:",Drama$RT_Score,"<br>","Audience Score:",Drama$A_Score,"<br>","Year:",Drama$Year))%>%
  add_markers()%>%
  layout(title="Scores for Oscar Nominated Dramas and Action Films (1980-2018)")


P2<-Action%>%
  plot_ly(x=~Action$RT_Score,y=~Action$A_Score,color=~Action$Decade,hoverinfo="text",
        text=~paste("Movie Title:",Action$Name,"<br>","RT Score:",Action$RT_Score,"<br>","Audience Score:",Action$A_Score,"<br>","Year:",Action$Year))%>%
  add_markers()%>%
  layout(showlegend=FALSE)

subplot(P1,P2,nrows=1)
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
Win <- read_csv("Win.csv") #Read Win
Movie <- read_csv("Movie.csv")#Read Movies
Year<-Movie$Year
NewMovies<-cbind(Critic,Audience,Year) ##Combine RT and Audience and Year

Average_Year<-aggregate(NewMovies,list(Year),mean) #Take the Average of each year

Winning<-Win$Winner #Winning Movie for Each Year

Time_series<-cbind(Average_Year,Winning) #Combine all Columns

Time<-data.frame(Time_series)


Time%>%
  plot_ly(x=~Time$Year,y=~Time$Critic,hoverinfo="text",
          text=~paste("Year:",Time$Year,"<br>","Average Score:",Time$Critic,"<br>","Best Picture",Winning))%>%
  add_lines() %>%
  layout(xaxis=list(title="Year (1980-2018)"),
         yaxis=list(title="Average Rotten Tomatoes Score"),
         title="Average RT Score for Oscar Nominated Films by Year")

Time%>%
  plot_ly(x=~Time$Year,y=~Time$Audience,hoverinfo="text",
          text=~paste("Year:",Time$Year,"<br>","Average Score:",Time$Audience,"<br>","Best Picture",Winning))%>%
  add_lines() %>%
  layout(xaxis=list(title="Year (1980-2018)"),
         yaxis=list(title="Average Rotten Tomatoes Score"),
         title="Average Audience Score for Oscar Nominated Films by Year")
